---
title: "R Project 1 - Hello R"
author: "Marcus Arzadon"
date: "9/16/2020"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1846 rows and 3 columns in the datasaurus_dozen file

### Exercise 2

First let's plot the data in the dino dataset:

The pipe operator: **%>%**, takes what comes before it and sends it as the first argument to what comesafter it. So here, we’re saying **filter** the **datasaurus_dozen** data frame for observations where **dataset =="dino"**.

Second, the assignment operator: <-, assigns the name dino_data to the filtered data frame

Last, the **ggplot** function is used to visualize the data 
**geom_point** is used to define which shape to use to mark/ represent each observation in the data

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

We need to calculate a summary statistic: the **correlation coefficient**.
**Correlation coefficient**, often referred to as *r* in statistics, measures the linear association between two variables. You will see that some of the pairs of variables we plot do not have a linear relationship between them. This is exactly why we want to visualize first: visualize to assess the form of the relationship, and
calculate r only if relevant. In this case, calculating a correlation coefficient really doesn’t make sense since the relationship between x and y is definitely not linear – it’s dinosaurial!

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

In the code below, we filter the data from datasaurus_dozen to observe where dataset=="star"

After plotting we can see a different picture than the plot previously which resemembles... you guessed, a star!

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

comparing the r of star to dino, star has a greater r by about .02
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Using the same data from datasaurus_dozen, by filtering out the dataset to find "circle", and after plotting, we get a picture of a circle!

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Here is the x and y correlation in the circle dataset
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)